### 2021-04-22 paper/ase21/overview.tex
[ASE21] Added compilation example in overview

\paragraph{Syntax and Semantics}
ECMAScript uses a variant of extended BNF notations to describe the JavaScript syntax.
While $\jiset$ synthesizes AST structures and JavaScript parsers from
the lexical and syntactic productions in ECMAScript, $\tool$ uses only
AST structures to define their types and access corresponding syntax-directed algorithms.
ECMAScript uses abstract algorithms written in a structured natural language to
describe the JavaScript semantics. While $\jiset$ compiles abstract algorithms to functions in $\ires$,
we modify $\ires$ to make it more suitable for type analysis as
formally defined in Section~\ref{sec:ires}.

>>>>

\paragraph{Syntax and Semantics}
ECMAScript uses a variant of extended BNF notations to describe the JavaScript syntax.
While $\jiset$ synthesizes AST structures and JavaScript parsers from
the lexical and syntactic productions in ECMAScript, $\tool$ uses only
AST structures to define their types and access corresponding syntax-directed algorithms.
ECMAScript uses abstract algorithms written in a structured natural language to
describe the JavaScript semantics.  $\jiset$ compiles such abstract algorithms to
$\ires$ functions with parameters and local variables.  For example, the
algorithm step
``\raisebox{-0.55ex}{\includegraphics[width=0.55\columnwidth]{img/compile-example}}''
is compiled to an $\ires$ instruction $\kwlet \; \code{baseObj} \code{=}
\escaped\!  \code{ToObject(V.Base)}$.  To make it more suitable for type
analysis, we modify $\ires$ as formally defined in Section~\ref{sec:ires}.
